\documentclass[10pt, oneside]{article} 
\usepackage{amsmath, amsthm, amssymb, calrsfs, wasysym, verbatim, bbm, color, graphics, geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{color}
\usepackage{tcolorbox}
\usepackage{geometry}
\geometry{tmargin=.75in, bmargin=.75in, lmargin=.75in, rmargin = .75in}  

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\Cdot}{\boldsymbol{\cdot}}
\newcommand{\solve}[1]{\setlength{\parindent}{0cm}\textbf{\textit{Proof: }}\setlength{\parindent}{1cm}#1 \hfill $\blacksquare$}

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{conv}{Convention}
\newtheorem{rem}{Remark}
\newtheorem{lem}{Lemma}[section]
\newtheorem{cor}{Corollary}


\title{Galois, Fields and Algebras}
\author{Naveensurya V \\ naveen24@iisertvm.ac.in}
\date{\today}

\begin{document}
	
	% \begin{center}
	% 	\textbf{Galois, Fields and Algebras}\\
	% 	by Dr. Viji Thomas\\ 
	% 	\LaTeX -ed by Naveensurya V

	% \end{center}
	
	\maketitle
	\tableofcontents
	
	\vspace{.25in}
	\pagebreak
	\section{First half of Galois Theory}
	
	\subsection{Basic Definitions}
	\begin{defn}
		Let $L / K$ be a field extension and \textbf{Automorphism} of $L/K$ is defined as \[Aut(L/K) := \{\phi : L \to L | \ \phi (k) = k , \ \forall k \in K \}\]
	\end{defn}

	\begin{defn}
		Let $U \subseteq Aut(L/K)$ then $\mathcal{F}(U)$ is defined as \[\mathcal{F}(U) := \{x \in L | \ \Psi (x)= x , \ \forall \Psi \in U\}\]
		
	\end{defn}
\begin{defn}
	Let $Z \subset L$ be a intermediate field between $L$ and $K$ then $\mathcal{G}(Z)$ is defined as
	\[ \mathcal{G}(Z) := Aut(L/Z) \]
\end{defn}

\begin{lem}
	Let $U \subseteq Aut(L/K)$ and $Z \subset L$ be a intermediate field between $L$ and $K$
	\begin{enumerate}
		\item[(a)] $U \subseteq \G \circ \F (U) := Aut(L/ \F(U))$
		\item[(b)] $Z \subseteq \F \circ \G (Z) $
		\item[(c)] $\F$ is inclusion reversing. i.e, $U_1 \subseteq U_2 \implies \F(U_2) \subseteq \F(U_1)$ 
		\item[(d)] $\G$ is inclusion reversing. i.e, $Z_1 \subseteq Z_2 \implies \G(Z_2) \subseteq \G(Z_1)$   
		\item[(e)] $\G = \G \circ \F \circ \G$
		\item[(f)] $\F = \F \circ \G \circ \F$   
	\end{enumerate}
\end{lem}
\begin{proof}
	Isn't it obvious $\heartsuit $
\end{proof}
	\subsection{Dedekind Theorem}
	\begin{thm}
		\textbf{[Dedekind's theorem on linear independence of characters.]}
		Distinct field automorphims \(\sigma_1, \dots , \sigma_n\) from $L \to L$ are linearly independent on the $L$-vector space of all mappings from $L \to L$ 

	\end{thm}
	\begin{proof}
		
	\end{proof}
\begin{defn}
	Let $L/K$ be a field extension. we can view $L$ as vector space over $K$ and \textbf{degree of extension} is defined as \[[L:K] := 
	dim_K(L)\] 

\end{defn}
\begin{lem}
	Suppose $[V_1:K] = n$ and $[V_2 :K] = m$, then \[dim_K\big(Hom_K(V_1, V_2)\big) = mn\]
\end{lem}

\begin{lem}
		Let $L/K$ be a finite field extension. Then $Aut(L/K) \le [L:K]$
	\end{lem}

\subsection{Artin Theorem}
\begin{defn}
	Let $U \subseteq Aut(L/K)$ be a finite subgroup. Then the \textbf{U-trace} of $\alpha \in L$ is defined as \[tr_U({\alpha}) := \sum_{\sigma \in U} \sigma(\alpha) \]
\end{defn}

\begin{lem}
	$tr_U : L \to \F(U)$ is a $K$-linear map. If $char(K) \nmid |U|$, then $tr_U:L \to \F(U)$ is surjective
\end{lem}
\begin{lem}
	$tr_U$ is not identitically zero.
\end{lem}

\begin{thm}
\textbf{[Artin]}
Let $U \subseteq Aut(L/K)$ be a finite subgroup. Then $[L : \F(U)] = |U|$ and $\G \circ \F (U)= U$ 

\end{thm}

\begin{proof}
Exercise. 	
\end{proof}

\begin{cor}
	If $L/K$ is a finite field extension , then $\G\circ\F \equiv  id$
\end{cor}

\subsection{Galois extension}
\begin{defn}
	An extension $L/K$ is \textbf{Galois extension} if \[\F \circ\G (K) = K \]
Equivalently, \( \F(Aut(L/(K))) = K \)	
\end{defn}

\begin{cor}
Let $G \subseteq Aut(L)$ be a finite subgroup and let $K := \F(G)$. Then $L/K$ is a galois extension and $Aut(L/K) = G$
\end{cor}
\begin{proof}
	
\end{proof}

\begin{cor}
	Let $L/K$ be a finite extension . Then $L/K$ is Galois $\iff |Aut(L/K)| = [L:K]$
\end{cor}

\section{Results from Ring Theory}

\end{document}
